### 2009-11-24 docs/marcello-dissertation/thesis/chapter1-introduction.tex
Fixing sentences, references, and misspelled words in chapters 1 and 2.
git-svn-id: svn://localhost/netbeams/branches/marcello/persistence@658 559edde2-a4d4-44e0-96fc-4035e40d7396

In order to provide access to the collected sensor data, different approaches
can be taken to interrogate sensor devices indirectly by accessing its data in
places called network sink. Similarly, the data model and database system
location may also influence in the process of reusing the collected data. In
this way, the lack of a persistence layer for existing sensor networks requires
a deep understanding about its infrastructure, the nature and location of the
collected data, the chosen data model representation, among others. For
instance, how can a data persistence layer safely represent the collected
sensor devices’ properties without the necessity of restructuring any existing
data model? Should the end users’ skills in database system be taken into
account or the use of programming languages to access the data
\cite{sn-programming-language}? This problem is currently faced by the
department of Biology at San Francisco State University with a marine sensor
network managed by researchers without Computer Science skills. While the data
access may enforce the difficulties, technical issues may also increase while
the implementation of a sensor network such as growth in terms of the number of
sensor devices and, consequently, the number of data produced. Last, but not
least, the way to read the data for reuse is the most striking features of the
sensor network, taking into account the different data formats used by the
primary users of the system. How can individual collected sensor data be
exported to other formats such as spreadsheets or archived files meant to be
shared among research peers? For these reasons, the inception of a persistence
storage can be an exceptionally challenging problem to solve.

In view of the fact that the persistence storage of a sensor network imposes
many different challenges, this work proposes the assessment of the current
state of the art for sensor networks in order to provide a data persistence
layer for an existing sensor network. As a matter of fact, this work’s first
contribution is the creation of a set of basic taxonomies for data persistence
in sensor networks, proposed to drive an empirical analysis of different
technologies used in the sensor network community. Furthermore, it also takes a
look at different alternatives not yet explored through experiments for a
selected sensor network as a case study. Similarly, this work makes another
novice contribution by suggesting a “lighter” data model and database
infrastructure that simply captures sensor network devices' observations,
taking into account the non-predictable scalability of its infrastructure, as
well as aspects of the nature of the data such as identity, time and location
of the collected data.

>>>>

In order to provide access to the collected sensor data, different approaches
can be taken to interrogate sensor devices indirectly by accessing its data in
places called network sink. Similarly, the data model and database system
location may also influence in the process of reusing the collected data. In
this way, the lack of a persistence layer for existing sensor networks requires
a deep understanding about its infrastructure, the nature and location of the
collected data, the chosen data model representation, among others. For
instance, how can a data persistence layer safely represent the collected
sensor devices' properties without the necessity of restructuring any existing
data model? Should the end users' skills in database system be taken into
account or the use of programming languages to access the data
\cite{sn-programming-language}? This problem is currently faced by the
department of Biology at San Francisco State University with a marine sensor
network managed by researchers without Computer Science skills. While the data
access may enforce the difficulties, technical issues may also increase while
the implementation of a sensor network such as growth in terms of the number of
sensor devices and, consequently, the number of data produced. Last, but not
least, the way to read the data for reuse is the most striking features of the
sensor network, taking into account the different data formats used by the
primary users of the system. How can individual collected sensor data be
exported to other formats such as spreadsheets or archived files meant to be
shared among research peers? For these reasons, the inception of a persistence
storage can be an exceptionally challenging problem to solve.

In view of the fact that the persistence storage of a sensor network imposes
many different challenges, this work proposes the assessment of the current
state of the art for sensor networks in order to provide a data persistence
layer for an existing sensor network. As a matter of fact, this work's first
contribution is the creation of a set of basic taxonomies for data persistence
in sensor networks, proposed to drive an empirical analysis of different
technologies used in the sensor network community. Furthermore, it also takes a
look at different alternatives not yet explored through experiments for a
selected sensor network as a case study. Similarly, this work makes another
novice contribution by suggesting a ``lighter" data model and database
infrastructure that simply captures sensor network devices' observations,
taking into account the non-predictable scalability of its infrastructure, as
well as aspects of the nature of the data such as identity, time and location
of the collected data.
